\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-06-28 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Finishing Section 4.3 ... now justwaiting for the simulations finishing to extract the relavant data and pics

\medskip
In order to investigate the impact of medium heterogeneity on formation and growth of viscous fingers, a numerical simulation was conducted using a distribution of permeability ({\bf K}) and viscosity ratio of 10. Absolute permeability ranging from 1.0$\times$10$^{-12}$ to 5.0$\times$10$^{-10}$ cm$^{2}$ (\ie 0.1 $\le$ {\bf K} $\le$ 50 milidarcy) was used in the simulation, which was conducted with the same mesh resolution, boundary and initial conditions as in the previous homogeneous cases. Figure~\ref{fig:HeleShawHeter_VR10} shows formation of fingers with continuous growth and coalescence of  dendritic fingers

In figure \ref{fig:HeleShawHeter_VR10}(a), there is the description of the domain. Three different cases with different set-ups will follow. The first one is the homogeneous domain where permeability $K_{1}=1.e-10$ everywhere while for the heterogeneous case the following permeabilities have been introduced, $K_{1}=(1.e-10 \;to\; 5.e-10$), $K_{2}=1.e-10$, $K_{3}=(1.e-11 \;to\; 5.e-10)$ and $K_{4}=(1.e-12 \;to\; 5.e-10)$. For the homogeneous case there are  two different mobility ratios of $3$ and $10$ while for the heterogeneous case only the case of  mobility ratio of $10$ will be investigated.

\medskip
As can been seen so far there is %from the fig.\ref{fig:1a_homoheleshaw_3}-%\ref{fig:1c_homoheleshaw_3}
%\ref{fig:2c_homoheleshaw_10} there is 
a significant difference on the flow pattern when the mobility ratio is $3$ and when it is $10$ under the same number of elements. %Figures \ref{fig:1a_homoheleshaw_3}, \ref{fig:1b_homoheleshaw_3}, \ref{fig:1c_homoheleshaw_3} 
The third case is of the Hele-Shaw cell simulation when $MR=10$ followed by the same initial and boundary conditions set-up, but now for a heterogeneous formation as this is described in figure \ref{fig:HeleShawHeter_VR10}. %\ref{fig:3b_heteheleshaw_10}-\ref{fig:3c_heteheleshaw_10}.  
 Fingers will be more profound and will start develop faster when the $MR=10$ compared to the uniform front that is developing when the $MR=3$ for the same time steps. In addition the flow patter of the fingers will be sharper and more intense when different regions with different permeabilities are introduced in the formation. The importance of this set-up is to understand how the simulation works and whether the flow pattern of the fingers follows the experimental results. Also how the fingers will be developed under different permeability schemes as these has already been experimentaly tested.

>>>>

\medskip
In order to investigate the impact of medium heterogeneity on formation and growth of viscous fingers, a numerical simulation was conducted using a distribution of permeability ({\bf K}) and viscosity ratio of 10. Absolute permeability ranging from 1.0$\times$10$^{-12}$ to 5.0$\times$10$^{-10}$ cm$^{2}$ (\ie 0.1 $\le$ {\bf K} $\le$ 50 milidarcy) was used in the simulation, which was conducted with the same mesh resolution, boundary and initial conditions as in the previous homogeneous cases. Figure~\ref{fig:HeleShawHeter_VR10} shows formation of multiscale elongations with continuous growth and coalescence of dendritic fingers. Finger width of approximately \red{XXX-XX} cm were obtained \red{(JG: COMPARE IT W THEORETICAL VALUE)}.
